The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-09 paper/Analisis.tex
minor changes in off center emission

\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation}
%
where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in a angular bin $\Delta
\Theta$. This definition satisfies the condition
$int_{-1}^{1}F(\mu)d\mu/2=1$.

@@

%As we know there is unlikely to find galaxies with radiation sources 
%distributed homogeneously. Most of them are in a clumpy distribution 
%(Laursen et al 2013*) which affected the resulting spectra. In order 
%to study an inhomogeneous distribution we set up a model in which we 
%select certain photons that are placed in a specific place but that 
%are not symmetrically distributed Fig.~\ref{figure:distributions} shows
%the distributions we set up.

@@

%In Fig.~\ref{figure:inhomogeneous} we show the resulting spectra of 
%distribution 1 and 2, the first effect we see is the asymmetry of the
%double peak, in the homogeneous and central distribution we see double
%peaks with the same height, while in this case one peak is higher than 
%the other. For $\tau=10^{5}$ we found that in distribution 1 the blueshifted
%peak is higher than the redshifted, and for distribution 2 the redshifted
%peak is the highest.

>>>>

\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation}
%
where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in a angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.

@@

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig. shows the distributions we 
set up, basically we take photons located in a sphere of $0.5 R$ and 
we moved $0.2 R$ in the x axis.

@@

%In Fig.~\ref{figure:inhomogeneous} we show the resulting spectra of 
%distribution 1 and 2, the first effect we see is the asymmetry of the
%double peak, in the homogeneous and central distribution we see double
%peaks with the same height, while in this case one peak is higher than 
%the other. For $\tau=10^{5}$ we found that in distribution 1 the blueshifted
%peak is higher than the reds~\ref{figure:distributionshifted, and for distribution 2 the redshifted
%peak is the highest.
